Measurement and Probability in Fuzzy Quantum Theories

### 2017-05-22 prop_iop.tex
prop_iop.tex \subsection{From Interval-valued to Real-valued} Added...

@@

@@

\begin{lemma}\label{lemma:QIVPM2QCM}Let $\mathscr{I}_{\mathrm{D}}$
be $\left\{ \imposs,\necess\right\} $. Given a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
then $\mu:\events\rightarrow\left[0,1\right]$ defined by 
\begin{equation} 
\mu(P)=\cases{ 
0 & if $\bar{\mu}(P)=\imposs$ ;\\ 
1 & if $\bar{\mu}(P)=\necess$
}\end{equation}
is a cryptodeterministic measure.\end{lemma}

\begin{proof}~
\begin{itemize}
\item Since $\bar{\mu}(\mathbb{0})=\imposs$, we have $\mu(\mathbb{0})=0$.
\item Since $\bar{\mu}(\mathbb{1})=\necess$, we have $\mu(\mathbb{1})=1$.
\item For every event $P$, we have 
\begin{equation}\eqalign{ 
& \pmeas\left(P\right)=0\\ 
\Rightarrow & \bar{\mu}(P)=\imposs\\
\Rightarrow & \bar{\mu}(\Omega\backslash P)=\left[1,1\right]-\imposs=\necess\\
\Rightarrow & \pmeas\left(\Omega\backslash P\right)=1=1-\pmeas\left(P\right)\textrm{ .}
}\end{equation}
Similarly, when $\pmeas\left(P\right)=1$, we also have $\pmeas\left(\Omega\backslash P\right)=1-\pmeas\left(P\right)$.
\item Given a collection $\left\{ P_{i}\right\} _{i=1}^{N}$ of pairwise
disjoint events. 
\begin{itemize}
\item If $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=1$, then we have $\necess=\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})$
so that $\necess=\sum_{i=1}^{N}\bar{\mu}(P_{i})$, i.e., $\sum_{i=1}^{N}\pmeas(P_{i})=1=\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)$.
\item If $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=0$, then we have $\imposs=\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})$
so that $\imposs=\sum_{i=1}^{N}\bar{\mu}(P_{i})$, i.e., $\sum_{i=1}^{N}\pmeas(P_{i})=0=\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)$.
\end{itemize}
\end{itemize}
\end{proof}

@@

\begin{cor}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
of dimension~$d\ge3$, there is no quantum interval-valued probability
measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $.\end{cor}

@@

\subsection{Quantum $\delta$-deterministic Probability Measures}

Since there is no quantum $\mathscr{I}_{\mathrm{D}}$-valued probability
measures, we want to know whether there is something which is almost
quantum $\mathscr{I}_{\mathrm{D}}$-valued probability measures. This
gives the following definition.

Given the preceding definition, theorem~\ref{thm:Kochen-Specker-expectation}
says there is no quantum $0$-deterministic probability measures.
In contrast, given a three-dimensional Hilbert space, there is $\frac{1}{3}$-deterministic
probability measures\nb$\iota_{\frac{1}{3}}\circ\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}:\events\rightarrow\left\{ \imposs,\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\necess\right\} $.
The real problem is if we decrease $\delta$ from $\frac{1}{3}$,
when quantum $\delta$-deterministic probability measures starts to
disappear?

>>>>

\subsection{From Real-valued to Interval-valued}

@@

\subsection{From Interval-valued to Real-valued}

@@

For example, recall $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
then a $\mathscr{I}_{\mathrm{D}}$-valued QIVPM is $0$-deterministic.
For another example, given a three-dimensional Hilbert space, $\iota_{\frac{1}{3}}\circ\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}:\events\rightarrow\left\{ \imposs,\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\necess\right\} $
is a $\frac{1}{3}$-deterministic. However, we will prove there is
no $\delta$-deterministic probability measures for smaller $\delta$
due to the Kochen-Specker theorem.

\begin{lemma}\label{lemma:QIVPM2QCM}Given a Hilbert space of dimension\nb$d$,
and a quantum $\delta$-deterministic probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
with $\delta<\left(1+d\right)^{-1}$, then $\mu:\events\rightarrow\left[0,1\right]$
defined by 
\begin{equation} 
\mu(P)=\cases{ 
0 & if $\bar{\mu}(P)\subseteq\left[0,\delta\right]$ ;\\ 
1 & if $\bar{\mu}(P)\subseteq\left[1-\delta,1\right]$
}\end{equation}
is a cryptodeterministic measure.\end{lemma}

\begin{proof}~
\begin{itemize}
\item Since $\bar{\mu}(\mathbb{0})=\imposs$, we have $\mu(\mathbb{0})=0$.
\item Since $\bar{\mu}(\mathbb{1})=\necess$, we have $\mu(\mathbb{1})=1$.
\item For every event $P$, we have 
\begin{equation}\eqalign{ 
& \pmeas\left(P\right)=0\\ 
\Rightarrow & \bar{\mu}(P)\subseteq\left[0,\delta\right]\\
\Rightarrow & \bar{\mu}(\mathbb{1}-P)=\left[1,1\right]-\bar{\mu}(P)\subseteq\left[1-\delta,1\right]\\
\Rightarrow & \pmeas\left(\mathbb{1}-P\right)=1=1-\pmeas\left(P\right)\textrm{ .}
}\end{equation}
Similarly, when $\pmeas\left(P\right)=1$, we also have $\pmeas\left(\mathbb{1}-P\right)=1-\pmeas\left(P\right)$.
\item Given a collection $\left\{ P_{i}\right\} _{i=1}^{N}$ of pairwise
orthogonal events, we must have $N\le d$. Also, $\delta<\left(1+d\right)^{-1}\Rightarrow\delta\le d\delta<1-\delta$.
\begin{itemize}
\item If $\pmeas(P_{i})=0$ for all $i$, then
\begin{equation}\eqalign{ 
& \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[0,N\delta\right]\subseteq\left[0,d\delta\right]\\
\Rightarrow & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[1-\delta,1\right]=\textrm{Ø}\Rightarrow\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\left[0,\delta\right]\\
\Rightarrow & \pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=0=\sum_{i=1}^{N}\pmeas(P_{i})\textrm{ .}
}\end{equation}
\item If $\pmeas\left(P_{i_{0}}\right)=1$ for a unique $i_{0}$, then
\begin{equation}\eqalign{ 
& \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[1-\delta,1+(N-1)\delta\right]\\
\Rightarrow & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[0,\delta\right]=\textrm{Ø}\Rightarrow\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\left[1-\delta,1\right]\\
\Rightarrow & \pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=1=\sum_{i=1}^{N}\pmeas(P_{i})\textrm{ .}
}\end{equation}
\item If $\pmeas\left(P_{i_{0}}\right)=\pmeas\left(P_{i_{1}}\right)=1$
for $i_{0}\ne i_{1}$, then
\begin{equation}\eqalign{ 
& \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[2-2\delta,N\right]\\
\Rightarrow & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[0,\delta\right]=\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[1-\delta,1\right]\textrm{Ø}\textrm{ .}
}\end{equation}
A contradiction! Therefore, this case is impossible, and need no further
discussion.
\end{itemize}
\end{itemize}
\end{proof}

@@

\begin{cor}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
of dimension\nb$d\ge3$, there is no quantum $\delta$-deterministic
probability measure for $\delta<\left(1+d\right)^{-1}$. When $\delta\ge\left(1+d\right)^{-1}$,
there exists a quantum $\delta$-deterministic probability measure
$\bar{\mu}:\events\rightarrow\mathscr{I}$ for some $\mathscr{I}$.\end{cor}

\begin{proof}...\end{proof}

@@
